---
title: "iteration_listcol"
author: "Amadeia Rector"
date: "10/30/2018"
output: github_document
---
```{r}
library(tidyverse)
library(rvest)
```

## for loops
-these are just vectors of numbers. will look like rectangle just a df
```{r}
df = data_frame(
  a = rnorm(20, 3, 1),
  b = rnorm(20, 0, 5),
  c = rnorm(20, 10, .2),
  d = rnorm(20, -3, 1)
)

is.list(df)
```
we asked if it's a list and it is

### let's get a function
-saw this previous class
-let's apply to df from above in next code chunk
-this is a list
```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```
apply function to df
-repeat multiple times
-is there a cleaner way
```{r}
mean_and_sd(df[[1]])
mean_and_sd(df[[2]])
mean_and_sd(df[[3]])
mean_and_sd(df[[4]])
```

### let's do this in a cleaner way with for loop
-input, output, and then need for loop to apply
-we want to avoid copy paste errors like below
```{r}
output = vector("list", length = 4)

mean_and_sd(df[[1]])
mean_and_sd(df[[2]])
mean_and_sd(df[[3]])
mean_and_sd(df[[4]])



for (i in 1:4) {
  output[[i]] = mean_and_sd(df[[i]])
}

output
```

## map statements

let's replace the for loop with map
-write a statement over this input collection, list...
-we'll get same as above
```{r}
output = map(df, mean_and_sd)
```

if you want to select what to apply function to
```{r}
df %>% 
  select(a,b,c) %>% 
  map(mean_and_sd)
```
```{r}
output = map(df, median)
```
 now with a different function
```{r}
output = map(df, summary)
```

## map variant
- creates a complete df
```{r}
output = map_df(df, mean_and_sd)
```

what if want to take look at output with median

-dbl because median outputs a single numeric value each time; the result is a vector instead of a list
```{r}
output = map_dbl(df, median)
```

## code syntax
-be **clear** about arguments
-let's switch it up
.x is list of atomic vector
.f is a function
naming input .x
```{r}
output = map(.x = df, ~mean(x = .x, na.rm = FALSE))
```

loading more than one thing
-see lecture


```{r}
read_page_reviews <- function(url) {
  
  h = read_html(url)
  
  title = h %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  stars = h %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  text = h %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()
  
  data_frame(title, stars, text)
}



url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)

read_page_reviews(vec_urls[[1]])
output = map(vec_urls, read_page_reviews)
```

## list columns
```{r}
library(rnoaa)

weather = 
  meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2016-01-01",
                      date_max = "2016-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
have data for each day for 3 stations
-we nest date within tmin
-we have a df!
-collapses data through tmin, because name and id just have three varying parts...
```{r}
# centralpark = weather %>% filter(...)
weather_nest =
weather %>% 
  nest(date:tmin)
```

```{r}
weather_nest %>% 
  pull(name)

weather_nest %>% 
  pull(id)

weather_nest %>% 
  pull(data)
```
 why is it usefull to have this? 
 may want to apply different things- tidy way to keep track of nesting structure - like a subdata... list of data frame inside another data frame. good if don't want to create multiple df

- you can unnest as well
#### unnest

```{r}
# centralpark = weather %>% filter(...)
weather_nest %>% 
  unnest
```

Look a LC elements
-can treat nest as df...
```{r}
weather_nest$data[[1]] %>% 
  skimr::skim()
```

fit a location specific regression
-fit in 3 regressions... repeated same line of code 3 times... could write a function
```{r}
lm(tmax ~ tmin, data = weather_nest$data[[1]])
lm(tmax ~ tmin, data = weather_nest$data[2]])
lm(tmax ~ tmin, data = weather_nest$data[[3]])
```

function: just apply to this dataset

```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}
```

```{r}
weather_lm(weather_nest$data[[1]])
```

map statement
-output gives linear model for the three stations
-this is using the nested df and the variable we are looking at is "data", which is actually a list!
```{r}
map(weather_nest$data, weather_lm)
```

Save output as a new list column...
-now have new column with linear model results...
-mutate creates a new variable...
so this works because only 3 rows are created for lm_results...
```{r}
weather_nest %>% 
  mutate(lm_results = map(data, weather_lm))
```

